Nail: A practical interface generator for data formats

### 2014-09-10 paper/osdi14/design.tex
4.2 nits

\paragraph{Parsing.}
\paragraph{Rules.}
A Nail grammar consists of rules that assign a parser to a name. Rules are written as assignments,
such as \cc{ints = /*parser definition*/}, which defines a rule called \cc{ints}. As we will
describe later in \S\ref{s:dependent} and \S\ref{s:transforms}, rules can optionally consume parameters.
Rules can be invoked in a Nail grammar anywhere a parser can appear. Rule invocations act as though
the body of the rule had been substituted in the code. If parameters appear, they are passed by
reference.
\paragraph{Integers and constraints.}

Nail's fundamental parsers represent signed or unsigned
integers with arbitrary lengths up to 64 bits.
Note that is possible to define parsers for sub-byte lengths, for example, the flag bits in the DNS
message header, in lines 4 through 8.

@@

The \emph{many} combinator takes a parser and applies it repeatedly
until it fails, returning an array of the inner parser's results. In line 39 of the DNS grammar, a
sequence of labels is parsed by parsing as many labels as possible, that is, until an invalid length
field is encountered.
The \emph{sepBy} combinator
additionally takes a constant parser, which it applies in between parsing
two values, but not before parsing the first value or after parsing the
last.  This is useful for parsing an array of items delimited by a separator.
%For examle, \cc{many uint8} represents an array of 8-bit unsigned
%integers, and \cc{sepBy uint8=',' (many uint8 | '0'..'9')} recognizes
%comma-separated lists of decimal numbers.

@@

\paragraph{Optional.}
Nail includes an \cc{optional} combinator, which attempts to recognize a value, but succeeds
without consuming input when it cannot recognize that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.
For example, the grammar for  Ethernet headers uses \cc{optional vlan\_header} to parse the VLAN
header that only appears in Ethernet packets transmitted to a non-default VLAN\@.

\paragraph{References.}
Rules allow for recursive grammars. To support recursive data types, we allow introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.
The reference combinator does not need to be used when another combinator, such as \cc{optional} or
\cc{many}, already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.

>>>>

\paragraph{Rules.}
A Nail grammar consists of rules that assign a parser to a name. Rules are written as assignments,
such as \cc{ints = /*parser definition*/}, which defines a rule called \cc{ints}. As we will
describe later in \S\ref{s:dependent} and \S\ref{s:transforms}, rules can optionally consume parameters.
Rules can be invoked in a Nail grammar anywhere a parser can appear. Rule invocations act as though
the body of the rule had been substituted in the code. If parameters appear, they are passed by
reference.
\paragraph{Integers and constraints.}

Nail's fundamental parsers represent signed or unsigned
integers with arbitrary lengths up to 64 bits.
Note that is possible to define parsers for sub-byte lengths, for example, the flag bits in the DNS
message header, in lines 5 through 8.

@@

The \cc{many} combinator takes a parser and applies it repeatedly
until it fails, returning an array of the inner parser's results. In line 39 of the DNS grammar, a
sequence of labels is parsed by parsing as many labels as possible, that is, until an invalid length
field is encountered.
The \cc{sepBy} combinator
additionally takes a constant parser, which it applies in between parsing
two values, but not before parsing the first value or after parsing the
last.  This is useful for parsing an array of items delimited by a separator.
%For examle, \cc{many uint8} represents an array of 8-bit unsigned
%integers, and \cc{sepBy uint8=',' (many uint8 | '0'..'9')} recognizes
%comma-separated lists of decimal numbers.

@@

\paragraph{Optional.}
Nail includes an \cc{optional} combinator, which attempts to recognize a value, but succeeds
without consuming input when it cannot recognize that value. Syntactically, \cc{optional} is
equivalent to a choice between the parser and an empty structure, but in the internal model it is
more concisely represented as a reference that is null when the parser fails.
For example, the grammar for  Ethernet headers uses \cc{optional vlan\_header} to parse the VLAN
header that appears only in Ethernet packets transmitted to a non-default VLAN\@.

\paragraph{References.}
Rules allow for recursive grammars. To support recursive data types, we introduce the
reference combinator \cc{*}  that does not change the syntax of the external format described, but
introduces a layer of indirection, such as a reference or pointer, to the model data type.
The reference combinator does not need to be used when another combinator, such as \cc{optional} or
\cc{many}, already introduces indirection in the data type. An example is shown in Figure~\ref{fig:grammar-arith}.
